\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-15 paper/paper.tex
pass through implementation and related work

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented a prototype implementation (Section~\ref{sec:implementation})
and deployed it on a 10~Gbps testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}).  In addition, \scheme provides significantly
more flexibility than existing Refraction protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

\subsection{Registration}

Clients can register intent to use the proxy in several covert ways. For
instance, they could use email~\cite{SWEET-ToN} or any other existing intermittently
available proxies
to register. In this section, we use a form of Refraction Networking similar to
TapDance to register directly with the station, though note our scheme is simpler and more
difficult to detect or block compared to vanilla TapDance.
%We note this form is simpler and more difficult to detect or block than
%TapDance.

@@

Once the phantom host IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the phantom host
\textbf{application}. The station ignores packets that are not from
the source IP address of the registering client, so that to a probing censor
from a different IP address,
the phantom host appears to be firewalled off from all but the client. We note
that this does not address censors that send follow-up probes, as censors could
take over the IP address of suspected clients for these
probes~\cite{ensafi-tor}. However, it does prevent censors from enumerating the
address space before hand, as they would have to do so from every potential
client IP address. Simply scanning the prefixes with ZMap~\cite{zmap13} from a
single vantage point would not reveal hosts that only respond to specific IPs
(e.g. are firewalled off).
%We instead address active probing in the application.

@@

Once the client has registered, packets sent to the phantom host IP address are
passed to the \textbf{application} running on the station. The application has
two main requirements: first, the protocol it uses to communicate with the
client must be difficult for the censor to passively detect and block by traffic
inspection. Second, the application must resist active probes by the censor (who
does not know the registration seed).

Any protocol that satisfies these criteria can be used as an application. For
instance, \texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
Tor~\cite{tor} that is designed to address both of these requirements:
it requires each endpoint to have knowledge of a
shared secret (which we can derive from the registration seed),
and attempts to be a protocol with no discernible
fingerprint. Probing censors that do not have the shared secret receive no
response, while clients that have the secret can communicate with the proxy.

@@

Besides obfs4, we next describe in detail several alternative application
protocols based on SSH, TLS, and WebRTC. These
alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
to support multiple application protocols. Should censors develop ways to
identify and block one protocol, others can still be used to provide proxy
access.

\subsubsection{Obfuscated SSH}

Obfuscated SSH~\cite{ossh} is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using a
regular expression, as there are no identifying headers or fields for a censor
to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
is then used to derive a symmetric key that encrypts the rest of the
communication. While this can be passively observable by censors (who can also
derive the key and deobfuscate the protocol), the key derivation is deliberately
slowed by an iterated hash to make such identifcation
expensive (though not impossible) at high speeds.

Obfuscated SSH also does not protect against active probing, as the censor can
easily create their own connections and confirm the server is using the
protocol. Nonetheless, this protocol is used successfully in deployed censorship
circumvention systems~\cite{psiphon}. Obfuscated SSH could also be used as a \scheme
application protocol, though we note it provides no active probing or passive
identifcation resistance.

\subsubsection{Mask Sites}

@@

\subsubsection{WebRTC}
\label{sec:webrtc}

@@

We implemented the \scheme protocol and deployed it at a 10~Gbps ISP
with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) phantom host address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

We used PF\_RING to load balance the 10~Gbps link over 4~CPU cores. PF\_RING
supports balancing across cores based on flow (5-tuple) or source and
destination IPs. However, both of these options present challenges for our 
implementation. One issue is that registrations could be processed on a
different core than the packets sent to that specific phantom host address. For
instance, a client could have its registration handled by Core 1, while its
packets to the phantom host address end up on Core 3, which doesn't know about the
original registration.

To address this, we used Redis~\cite{redis} to allow each process to announce
(publish) newly registered decoys to the other cores so they can
add them to their local list of registered phantom host addresses.
However, this introduces two new problems. First, a core might add a
registration \emph{after} it has already received and processed packets destined
for the specified phantom host. This typically isn't a problem when running on a
single core, as packets are processed sequentially. Second, each core may
timeout each phantom host at different times, potentially leading to differing
behavior that is visible to a censor. For instance, if we used the
source/destination IPs to load balance, a censor's packets to a phantom host could
be processed by a different core than the client. If the censor waits for the
known timeout before sending a probe, its core may have timed out that phantom host, while the client's core has refreshed the timeout of the phantom host due
to active use.

To address the first issue, we force the client to delay sending its connection
to the phantom host until a short time after registration. In practice, we force
the client to wait until the registration decoy responds before starting a
connection with the registered phantom host.

To address the second issue, we implemented a new load-balancing algorithm in
PF\_RING to select the core based solely on the destination IP address of the
packet. This still means we must use Redis to tell all of the cores of new
registrations, but that only one core will be responsible for processing all of
the packets sent to a given phantom host, regardless of who or when it is sent.

@@

Our client is also written in Golang, and uses a TapDance-like protocol for
registration. We note that this protocol should be harder for censors to observe
because it consists of only a single (complete) request, and the station does
not have to spoof packets as the decoy used during registration, only passively
observe them.

After registering, the client connects to the derived phantom host address, and
switches secrets after the handshake. At this point, a local application (e.g.
SOCKS client) can connect to the client, and it will transparently be connected to
the remote end via the encrypted phantom host connection.

\if0
In order to scale up to 10Gbps and beyond,
one has to utilize multiple cores and employ load balancing.
We use PF\_RING built-in load balancer \emph{zbalance} to efficiently
distribute load between 4 cores.
Our timeout is based on last IP address usage time, which prevents us from
balancing load based on source IP address,
as censor would be able to observe
same destination IP address picking or not picking up
depending on source IP address.
To avoid such unusual behavior we balance on destination IP.
Since PF\_RING does not feature load balancing based only on destination
IP address, we made a custom implementation of this zbalance policy.

TODO: say it's tested on 10 Gbps

@@

To evaluate our \scheme implementation, we compare its bandwidth
to that of TapDance in a realistic ISP setting. We used a full duplex 10~Gbps
network tap at a mid-sized ISP and run both implementations on a 1U server with
an 8-core Intel Xeon E5-2640 CPU, 64GB of RAM, and a dual-port Intel X710 10GbE SFP+
network interface. A typical week of bandwidth seen on the tap is
shown in Figure~\ref{fig:tap-bandwidth}, ranging from 2.4~Gbps to peaks above
17~Gbps.

@@

\paragraph{ICMP}
Censors can use ping or traceroute utilities (via ICMP) to probe potential phantom
hosts. Because there is (usually) no host at the phantom host address, these
probes will timeout and produce no response. They might also produce
``Destination Unreachable'' responses from routers depending on how they are
configured. We performed a scan of 10~million IPv6 addresses in a routable /32
prefix to see if it is common to respond with such tell-tale ICMP messages for
unused messages. We found only 0.016\% of addresses responded with any ICMP
messages (a combination of ``Time Exceeded'' and ``Destination Unreachable'').

@@

\paragraph{Address entropy}
Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
For instance, google.com has the address
\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}). Only 24 bits are set to 1 in this address,
giving censors a possible feature to filter on: addresses that have too much
entropy (or even simply bits set) could be suspicious as phantom hosts. To demonstrate and quantify
this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
notably skewed to less than expected if addresses were randomly generated. However, there
are still a significant number of networks that appear to have random-looking addresses,
making it difficult for censors to block these addresses outright. For a specific deployment,
operators should be careful to observe the distribution of addresses in the subnets they use,
and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).

>>>>

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented Conjure (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}).  In addition, \scheme provides significantly
more flexibility than existing Refraction protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

\subsection{Registration}
\label{sec:registration}
Clients can register intent to use the proxy in several covert ways. For
instance, they could use email~\cite{SWEET-ToN} or any other existing intermittently
available proxies
to register. In this section, we use a form of Refraction Networking similar to
TapDance to register directly with the station, though note our scheme is simpler and more
difficult to detect or block compared to vanilla TapDance.
%We note this form is simpler and more difficult to detect or block than
%TapDance.

@@

Once the phantom host IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the phantom host
\textbf{application}. The station only forwards packets that originate from the
IP address of the registering client, making the phantom host appear as
firewalled off to everyone but the client.
We note that censors have been observed taking over client IP
addresses for follow-up probing~\cite{ensafi-tor}, which would allow censors to
still communicate with registered phantom hosts despite this filter.
However, filtering in this way does prevent censors from enumerating the
address space before hand, as they would have to do so from every potential
client IP address. Simply scanning the prefixes with ZMap~\cite{zmap13} from a
single vantage point would not reveal hosts that only respond to specific IPs
(e.g. are firewalled off).
%We instead address active probing in the application.

@@

Once the client has registered, packets sent to the phantom host IP address are
passed to the \textbf{application} running on the station, which provides
proxy access to the client. The application has
two main requirements: first, the protocol it uses with the client 
must be difficult for the censor to \emph{passively detect} and block by traffic
inspection. Second, the application must resist \emph{active probes} by the censor (who
does not know the registration seed).

Any protocol that satisfies these criteria can be used as an application. In
this section, we describe existing protocols (obfs4 and obfuscated SSH) as well
as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
can be used in \scheme, and evaluate how each meet the necessary requirements.
Figure~\ref{fig:overview} describes a high-level overview of the \scheme
registration and application behavior.

\subsubsection{obfs4}

\texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
Tor~\cite{tor} designed to resist both passive detection and active probing.
Traffic is obfuscated by encrypting it and sending headerless ciphertext
messages, and clients can only connect to \texttt{obfs4}
servers by proving knowledge of a secret. Probing censors that do not have the
secret get no response from \texttt{obfs4} servers, making it difficult for
censors to confirm if a host is a proxy. Server IPs and their corresponding secrets
are normally distributed out-of-band through Tor's bridge distribution system.

We can adopt \texttt{obfs4} for use as a \scheme application, with minimal
modification. During
registration, the \scheme client and station can use the registration seed to
derive the \texttt{obfs4} secrets (NODE\_ID and server private/public keys)
needed for the client to connect. The station then launches an \texttt{obfs4} server
instance at the registered phantom address, and the client can connect to it using the
derived secrets. If a censor attempts to connect to the phantom address (even
using the client's IP), it will not receive a response, as it does not know the
registration seed used to derive the \texttt{obfs4} secrets.

Using \texttt{obfs4} as a \scheme application has the added benefit that servers
and secrets do not need to be distributed out-of-band, eliminating one of the
main ways censors currently block existing \texttt{obfs4}
instances~\cite{tor-bridge-blocking-blog}. Instead, each \scheme \texttt{obfs4}
instance is private to its registering client, and there is no public service
that censors can use to discover them.

@@

%Besides obfs4, we next describe in detail several alternative application
%protocols based on SSH, TLS, and WebRTC. These
%alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
%to support multiple application protocols. Should censors develop ways to
%identify and block one protocol, others can still be used to provide proxy
%access.

\subsubsection{Obfuscated SSH}
\label{sec:ossh}

Obfuscated SSH~\cite{ossh} is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using basic
packet filters, as there are no identifying headers or fields
to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
is then used to derive a symmetric key that encrypts the rest of the
communication. While this can passively detected by censors (who can also
derive the key and deobfuscate the protocol), the key derivation is deliberately
slowed by an iterated hash to make such identifcation
expensive (though not impossible) at high speeds.

Obfuscated SSH also does not protect against active probing, as the censor can
easily create their own connections and confirm the server is using the
protocol. Nonetheless, this protocol is still used successfully in deployed censorship
circumvention systems~\cite{psiphon}. Obfuscated SSH can also be used as a \scheme
application protocol, though we note it provides no active probing or passive
identifcation resistance.

\subsubsection{Mask Sites}
\label{sec:mask-sites}

@@

\subsubsection{Phantom WebRTC Clients}
\label{sec:webrtc}

@@

We implemented the \scheme protocol and deployed a station at a
20~Gbps router in a mid-sized transit ISP. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) phantom host address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

To achieve high-performance necessary to operate at 20~Gbps, we used
PF\_RING~\cite{pfring} to load balance incoming packets over 4~CPU cores. PF\_RING
supports balancing across cores based on flow (5-tuple) or source and
destination IPs. However, both of these options present engineering challenges
for \scheme that we must overcome.
One issue is that registrations could be processed on a
different core than the packets sent to that specific phantom host address. For
instance, a client could have its registration handled by Core 1, while its
packets to the phantom host address end up on Core 3, which doesn't know about the
original registration.

To address this, we used Redis~\cite{redis} to allow each process to broadcast
(publish) newly registered decoys to the other cores so they can
add them to their local list of registered phantom host addresses.
However, this introduces two new problems. First, a core might add a
registration \emph{after} it has already received and processed packets destined
for the specified phantom host. This typically isn't a problem when running on a
single core, as packets are processed sequentially. Second, each core may
timeout each phantom host at different times, potentially leading to differing
behavior that is visible to a censor. For instance, if we used the
source/destination IPs to load balance, a censor's packets to a phantom host could
be processed by a different core than the client. If the censor waits for the
known timeout before sending a probe, its core may have timed out that phantom host, while the client's core has refreshed the timeout of the phantom host due
to active use.

To address the first issue of asynchronous cores, we force the client to delay sending its connection
to the phantom host until a short time after registration. In practice, we force
the client to wait until the registration decoy responds before starting a
connection with the registered phantom host. While the decoy response is
unrelated to the station's processing, it serves as a conservative way to know
the registration has had time to reach the station.

To address the second issue of differing core timeouts, we implemented a new
load-balancing algorithm in
PF\_RING to select the core based solely on the destination IP address of the
packet. We still must use Redis to tell all of the cores of new
registrations, but only one core will be ultimately responsible for processing all of
the packets sent to a given phantom host, regardless of who or when it is sent.

@@

%TODO: how many registration requests do we make? how long does it take?
We created a \scheme client and integrated it with the Psiphon~\cite{psiphon}
anticensorship client. Psiphon has millions of users in censored countries, and
we are in the early stages of rolling \scheme out to real-world users.

Our \scheme client is written in Golang, and uses the TapDance-like protocol
(Section~\ref{sec:registration}) for
registration. We note that this protocol should be harder for censors to observe
than normal TapDance because it consists of only a single (complete) request, and the station does
not have to spoof packets as the decoy used during registration, only passively
observe them.

We implemented two of the applications in our client: Obfuscated SSH used by
Psiphon
(Section~\ref{sec:ossh}) and our Mask Site protocol
(Section~\ref{sec:mask-sites}). Our client signals which application it will use
in the registration tag. After registration, the client connects to the derived
phantom host address, and speaks the specified application protocol, which
tunnels a SOCKS connection between the client and Psiphon's backend servers,
which proxy the client's connections.

\if0
In order to scale up to 20Gbps and beyond,
one has to utilize multiple cores and employ load balancing.
We use PF\_RING built-in load balancer \emph{zbalance} to efficiently
distribute load between 4 cores.
Our timeout is based on last IP address usage time, which prevents us from
balancing load based on source IP address,
as censor would be able to observe
same destination IP address picking or not picking up
depending on source IP address.
To avoid such unusual behavior we balance on destination IP.
Since PF\_RING does not feature load balancing based only on destination
IP address, we made a custom implementation of this zbalance policy.

TODO: say it's tested on 20 Gbps

@@

To evaluate our \scheme implementation, we compare its bandwidth
to that of TapDance in a realistic ISP setting. We used a 20~Gbps
network tap at a mid-sized ISP and run both implementations on a 1U server with
an 8-core Intel Xeon E5-2640 CPU, 64GB of RAM, and a dual-port Intel X710 10GbE SFP+
network interface. A typical week of bandwidth seen on the tap is
shown in Figure~\ref{fig:tap-bandwidth}, ranging from 2.4~Gbps to peaks above
17~Gbps.

@@

\paragraph{ICMP}
Censors can use ping or traceroute utilities (via ICMP) to probe potential phantom
hosts. Because there is (usually) no host at the phantom host address, these
probes will timeout and produce no response. They might also produce
``Destination Unreachable'' responses from routers depending on how they are
configured. We performed a scan of 10~million IPv6 addresses in a routable /32
prefix to see if it is common to respond with such tell-tale ICMP messages for
unused messages. We found only 0.016\% of addresses responded with any ICMP
messages (mainly ``Time Exceeded'' and ``Destination Unreachable'').

@@

\paragraph{Address entropy}
Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
For instance, google.com has the address
%\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}. Only 24~bits are set to 1 in this address,
giving censors a possible feature to filter on: addresses that have too much
entropy (or even simply bits set) could be suspicious as phantom hosts. To demonstrate and quantify
this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
notably skewed to less than expected if addresses were randomly generated. However, there
are still a significant number of networks that appear to have random-looking addresses,
making it difficult for censors to block these addresses outright. For a specific deployment,
operators should be careful to observe the distribution of addresses in the subnets they use,
and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).

### 2019-05-15 paper/related.tex
pass through implementation and related work

Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor. Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this information secret is challenging; additionally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations. \scheme furthers this goal by creating a large number of destinations out of the dark space. A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations. CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication. As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number. In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}

>>>>

Traditionally, proxies deployed for censorship are eventually identified and
blocked by the censor. Several proposals have been made to carefully control
the distribution of proxy addresses, using social connections and
reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this
information secret is challenging; additionally, censors often employ active
scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction
networking generally assumes that clients have no secret information, and
instead relies on the  collateral damage that would result from blocking all
the potential decoy destinations. \scheme furthers this goal by creating a
large number of destinations out of the dark space. A similar approach was
conceptualized in DEFIANCE~\cite{lincoln2012}, where censored Tor clients
connect to pools of addresses that are volunteered to run Tor bridge nodes.
Unlike \scheme, DEFIANCE requires network admins that own the IP blocks to
participate and operate proxies on their addresses, allowing censors to block
the IP ranges involved once discovered. In contrast, \scheme can be
deployed at transit ISPs, and censors face a large risk of collateral
over-blocking if they block the network blocks used.
Another similar approach was
taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large
set of dummy destinations. CensorSpoofer, however, could only send information
in one direction---to the client---and had to rely on a separate out-of-band
channel for client-to-proxy communication. As an alternative approach,
FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to
run Flash- or WebRTC-based proxies within their browser to allow censored users
to connect to the Tor network with the potential to greatly increase the
number. In practice, these proxies served a very small number of users, as
compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}
